Consistent Polyhedral Surrogates via Embedding

### 2019-07-28 notes/top-k.tex
typos

First, we break this into three cases:
\begin{enumerate}
	\item [$y > k$] Here, we observe that $L^{top-k}(u)_y = (1-u_y + \bar{u})_+ > 0$ for all $u$ given our assumptions, so we don't need to worry about the $\max(\cdot,0)$ operation.
	\item [$y \leq k$, $u_y \leq 1$] Here, $\min(u_y,1) = u_y$, so we can rewrite the loss as $L^{top-k}(u)_y = (1 - \frac {k+1}{k} u_y + \bar u)_+$, which always has the inside term nonnegative.
	\item [$y \leq k$, $u_y > 1$] The term inside $\cdot_+$ of $L^{top-k}(u)_y$ is nonnegative and equal to $1 - \frac 1 k - u_y + \ubar$ when $u_y \leq \bar{u}_{-y} + 1$, and $0$ if $u_y \geq \bar{u}_{-y} + 1$.
\end{enumerate}

@@

We can now write the expected loss as follows:
\begin{align*}
\inprod{p}{L^{top-k}(u)} &= \sum_{y=1}^n p_y L^{top-k}(u)_y \\
&= \sum_{y=1}^t p_y L^{top-k}(u)_y + \sum_{y=t+1}^b p_y L^{top-k}(u)_y + \sum_{y=b+1}^k p_y L^{top-k}(u)_y + \sum_{y=k+1}^n p_y L^{top-k}(u)_y\\
&= 0 + \sum_{y=t+1}^b p_y (1 - \frac 1 k - u_y + \ubar) + \sum_{y=b+1}^k p_y (1 - \frac{k+1} k u_y + \ubar) + \sum_{y=k+1}^n p_y(1-u_y + \ubar)\\
\end{align*}
Moreover, substituting $j=0$, we can simplify further:
\begin{align*}
&= 1 + \ubar - \inprod{p}{u} - \inprod{p \odot \Ind{y \leq i}}{\frac 1 k \ones} - \inprod{p \odot \Ind{i+1 \leq y \leq k}}{ \frac u k}\\
&= 1 + \ubar - \inprod{p \odot \Ind{y \leq i}}{\frac 1 k \ones + u} - \inprod{p \odot \Ind{i+1 \leq y \leq k}}{ \frac {k+1} k u}\\
\end{align*}
When considering the Bayes Risk, we use this final form of the expected loss.

>>>>

First, we break this into three cases:
\begin{enumerate}
	\item $y > k$. Here, we observe that $L^{top-k}(u)_y = (1-u_y + \bar{u})_+ > 0$ for all $u$ given our assumptions, so we don't need to worry about the $\max(\cdot,0)$ operation.
	\item $y \leq k$, $u_y \leq 1$. Here, $\min(u_y,1) = u_y$, so we can rewrite the loss as $L^{top-k}(u)_y = (1 - \frac {k+1}{k} u_y + \bar u)_+$, which always has the inside term nonnegative.
	\item $y \leq k$, $u_y > 1$. The term inside $\cdot_+$ of $L^{top-k}(u)_y$ is nonnegative and equal to $1 - \frac 1 k - u_y + \ubar$ when $u_y \leq \bar{u}_{-y} + 1$, and $0$ if $u_y \geq \bar{u}_{-y} + 1$.
\end{enumerate}

@@

We can now write the expected loss as follows:
\begin{align*}
\inprod{p}{L^{top-k}(u)} &= \sum_{y=1}^n p_y L^{top-k}(u)_y \\
&= \sum_{y=1}^t p_y L^{top-k}(u)_y + \sum_{y=t+1}^b p_y L^{top-k}(u)_y + \sum_{y=b+1}^k p_y L^{top-k}(u)_y + \sum_{y=k+1}^n p_y L^{top-k}(u)_y\\
&= 0 + \sum_{y=t+1}^b p_y (1 - \frac 1 k - u_y + \ubar) + \sum_{y=b+1}^k p_y (1 - \frac{k+1} k u_y + \ubar) + \sum_{y=k+1}^n p_y(1-u_y + \ubar)\\
\end{align*}
Moreover, substituting $t=0$, we can simplify further:
\begin{align*}
&= 1 + \ubar - \inprod{p}{u} - \inprod{p \odot \Ind{y \leq i}}{\frac 1 k \ones} - \inprod{p \odot \Ind{i+1 \leq y \leq k}}{ \frac u k}\\
&= 1 + \ubar - \inprod{p \odot \Ind{y \leq i}}{\frac 1 k \ones + u} - \inprod{p \odot \Ind{i+1 \leq y \leq k}}{ \frac {k+1} k u}\\
\end{align*}
When considering the Bayes Risk, we use this final form of the expected loss.
